---
title: "Analyzing Aggravated Burglaries in Davidson County"
output: html_notebook
---

```{r}
library(sf)
library(tidyverse)
```

Part 1: Data Preparation

You've been provided three datasets for this project:

burglaries_2023.csv: Contains data on the aggravated burglary incidents in Davidson County. This was obtained from https://data.nashville.gov/Police/Metro-Nashville-Police-Department-Incidents/2u6v-ujjs.
census.csv: Census tract level data on population and median income. This was obtained from the US Census American Community Survey.
DC: A shapefile containing Davidson County census tracts
Perform a spatial join to determine the census tract in which each burglary occurred. Hint: You may want to make use of the st_as_sf function in order to convert the burglaries data into an sf object.

After performing the spatial join, merge in the census data. Note: Make sure that the final dataset contains all census tracts.

```{r}
census_tract <- st_read('../data/DC/DC.shp')
```

```{r}
burglaries <- read_csv("../data/burglaries_2023.csv") |> 
  filter(!latitude < 35)
```
```{r}
census_tract |> 
  distinct(TRACTCE) |> 
  nrow()
```

```{r}
burglaries_sp <- st_as_sf(burglaries |> drop_na(latitude),
         coords = c("longitude", "latitude"), crs = st_crs(census_tract)
         )
```

```{r}
census_tract |> 
  ggplot() +
  geom_sf() +
  geom_sf(data = burglaries_sp, size = 0.1)
```
No points outside Nashville are present.

```{r}
burg_loc <- st_join(census_tract, burglaries_sp, join = st_contains)
```

```{r}
burg_loc |> 
  distinct(TRACTCE) |> 
  nrow()
```

```{r}
census <- read_csv("../data/census.csv", col_types = cols(state = "c", county = "c"))
```

```{r}
burg_loc <- inner_join(burg_loc, census, join_by(TRACTCE == tract, STATEFP == state, COUNTYFP == county))
```

```{r}
burg_loc |> 
  distinct(TRACTCE) |> 
  nrow()
```






Part 2 - Exploratory Analysis
Perform some exploratory analysis on your prepared dataset.

Aggregate the data by census tract. Warning: each incident can appear multiple times if there are multiple victims, so be sure that you aren't double-counting any incidents.

Which census tract had the highest number of burglaries? Which census tract had the highest number of burglaries per 1000 residents?

We're interested in the relationship between median income and number of aggravated burglaries, so examine those variables on their own and together to see what you can find. You may want to perform additional calculations, create plots, etc.


Drop duplicate incidents since we aren't considering the number of victims. If that were a factor, the better approach would be grouping by everything except victim number and adding a column with a count of rows (or at least that's what I would do in SQL).
```{r}
burg_distinct <- burg_loc |> 
  distinct(incident_number, .keep_all = TRUE)
```
895 distinct incidents

Census tract with most burglaries
```{r}
burg_distinct |> 
  st_drop_geometry() |> 
  group_by(TRACTCE) |> 
  count(name = "num_burglaries") |> 
  arrange(desc(num_burglaries))
```

highest number of burglaries per 1000 residents
```{r}

```

