---
title: "Analyzing Aggravated Burglaries in Davidson County"
output: html_notebook
---

```{r}
library(sf)
library(tidyverse)
```

Part 1: Data Preparation

You've been provided three datasets for this project:

burglaries_2023.csv: Contains data on the aggravated burglary incidents in Davidson County. This was obtained from https://data.nashville.gov/Police/Metro-Nashville-Police-Department-Incidents/2u6v-ujjs.
census.csv: Census tract level data on population and median income. This was obtained from the US Census American Community Survey.
DC: A shapefile containing Davidson County census tracts
Perform a spatial join to determine the census tract in which each burglary occurred. Hint: You may want to make use of the st_as_sf function in order to convert the burglaries data into an sf object.

After performing the spatial join, merge in the census data. Note: Make sure that the final dataset contains all census tracts.

```{r}
census_tract <- st_read('../data/DC/DC.shp')
```

```{r}
burglaries <- read_csv("../data/burglaries_2023.csv")
```
```{r}
census_tract |> 
  distinct(TRACTCE) |> 
  nrow()
```

```{r}
burglaries_sp <- st_as_sf(burglaries |> drop_na(latitude),
         coords = c("longitude", "latitude"), crs = st_crs(census_tract)
         )
```

```{r}
burg_loc <- st_join(census_tract, burglaries_sp, join = st_contains)
```

```{r}
burg_loc |> 
  distinct(TRACTCE) |> 
  nrow()
```


